### 2023-01-14 code/plots.Rmd
auto select best_e

escapement |> 
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))

esc_sims <- escapement |> 
  filter(action == 0.58) |>
  rename(escapement = action) |>
  mutate(effort = pmax(1 - escapement / (sp1+1), 0))

>>>>

best_e <- escapement |> 
  group_by(action, rep) |>
  filter(t == max(t)) |> 
  group_by(action) |>
  summarise(reward = mean(reward)) |> 
  filter(reward == max(reward))

esc_sims <- escapement |> 
  filter(action == best_e$action) |>
  rename(escapement = action) |>
  mutate(effort = pmax(1 - escapement / (sp1+1), 0))
